Normalized Coherence

### 2019-09-30 Analysis/03_Normalized_Coherence.Rmd
Disable saving to text files

# Write general function for saving runs to .csv

```{r}
save_norm_coh = function(coherence_tab, num_msig, num_rand, run, database) {
  require(dplyr)
  fileNameOut <- file.path("./data/Coherence_Results/", paste0("coherence_msig_",database,"_",num_msig, "_rand_", num_rand, "_", run, ".csv"))
  write_csv(coherence_tab, fileNameOut)
}
```

# Save the runs in .csv form

```{r}
#Saving biogrid results to csv
save_norm_coh(norm_coh_biogrid, num_msig = num_msig, num_rand = num_rand, run = run, database = "Biogrid")

>>>>

```{r eval=FALSE}
# Write general function for saving runs to .csv

save_norm_coh = function(coherence_tab, num_msig, num_rand, run, database) {
  require(dplyr)
  fileNameOut <- file.path("./data/Coherence_Results/", paste0("coherence_msig_",database,"_",num_msig, "_rand_", num_rand, "_", run, ".csv"))
  write_csv(coherence_tab, fileNameOut)
}

# Save the runs in .csv form
#Saving biogrid results to csv
save_norm_coh(norm_coh_biogrid, num_msig = num_msig, num_rand = num_rand, run = run, database = "Biogrid")
